Transport map accelerated-PAIS, and application to inverse problems arising from multiscale stochastic reaction networks

### 2017-07-11 TPAIS.tex
Added some more stuff to the beginning of Section 2

In this section we give details on how \cite{parno2014transport} propose to couple the target,
$\mu_{\theta}$, with the reference distribution, $\mu_r$. When sampling, ideally we would like to draw a sample directly from the target distribution. When we have the exact map, $T\in\mathcal{T}$, $T\colon \mathcal{X}\rightarrow\mathbb{R}^d$, we are able to map samples from the posterior distribution onto a reference density, $\pi_r$ which is a standard Gaussian. We can then draw a proposal sample from $\pi_r$, before mapping these samples back onto target space using $T^{-1}$. These proposed samples are distributed according to the target distribution. On target space, the proposal distribution is induced by the pullback of the standard Gaussian through the map,
\begin{equation}\label{eq:pullback}
	\tilde{\pi}(\theta) = \pi_r(T(\theta))|J_T(\theta)|,
\end{equation}
which is equal to the target density when $T$ is exact. Clearly we require $T$ to be monotonic and have continuous first derivatives, which means that our space of feasible transference plans, $\mathcal{T}^\uparrow$, may not include the exact map. Since it is unlikely that $T\in\mathcal{T}^\uparrow$, we are motivated to formulate an optimisation problem as discussed in Section~\ref{sec:intro_optim}.

>>>>

In this section, we give details on how we have adapted the method
proposed in \cite{parno2014transport} to couple the target,
$\mu_{\theta}$, with the reference distribution, $\mu_r$. In many
applications ***REFS*** inverse problems arise which lead to posterior
distributions from which it is challenging to sample efficiently. This
can be due to multimodality, strong correlations between parameters,
or vastly different scales of sensitivity in different directions, for
example the concept of sloppy models. Standard random walks become
inefficient in this context since the proposal distributions do not
take into account these types of challenging structures in the
density, leading to a large number of proposals being made in low
density regions.

One way that this can be tackled is to implement more complex MCMC
methods which are able to explore the state space more
efficiently. For example the Metropolis-Adjusted Langevin Algorithm (MALA) or Hamiltonian Monte
Carlo (HMC) methods use gradient information about the target density
in order to make proposals in better directions that RWMH. Riemannian
manifold MCMC methods can use additionally approximations of the
Hessian of the target in order to make very large moves with a good
probability of being accepted.

Another approach is the simplification of the posterior density
itself. In \cite{parno2014transport}, the authors proposed the
approximation of an invertible map which exactly couples the postieror distribution
$\mu_{\theta}$ to a reference measure $\mu_r$. Given such a map,
$T\in\mathcal{T}$, $T\colon \mathcal{X}\rightarrow\mathbb{R}^d$, we can then draw a proposal sample from $\pi_r$, before mapping these samples back onto target space using $T^{-1}$. These proposed samples are distributed according to the target distribution. On target space, the proposal distribution is induced by the pullback of the standard Gaussian through the map,
\begin{equation}\label{eq:pullback}
	\tilde{\pi}(\theta) = \pi_r(T(\theta))|J_T(\theta)|,
\end{equation}
which is equal to the target density when $T$ is exact. Clearly we
require $T$ to be monotonic and have continuous first derivatives,
which means that our space of feasible transference plans,
$\mathcal{T}^\uparrow$, may not include the exact map. Since it is
unlikely that $T\in\mathcal{T}^\uparrow$, we are motivated to
formulate an optimisation problem as discussed in
Section~\ref{sec:intro_optim}.  ****PAUL, what is
$\mathcal{T}^\uparrow$, what is in Section~\ref{sec:intro_optim}*****
